Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-10 chi/piecework/presentation/complexity.tex
checkin wednesday morning

\begin{frame}{What Does On--Demand Work Say?}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      Build complexity into the process
      \begin{itemize}
        \item<+-> Apply CS methods to people\par
                 \scriptsize{\textcite{crowdForgeKittur}\par}\normalsize{}
        \item<+-> Humans as computational units\par
                 \scriptsize{\textcite{Lasecki:2014:LSR:2661334.2661352}\par}\normalsize{}
        \item<+-> Crowdsourcing workflows as function state machines\par
                 \scriptsize{\textcite{latoza2014microtask}\par}\normalsize{}
      \end{itemize}
    \end{column}

    \begin{column}{0.4\textwidth}
      \only<1>{
      \includegraphics[max width=\textwidth,max height=\textheight]{figures/complexity/cw_literature/mapReduce.png}
      }

      \only<2>{
        \includegraphics[max width=\textwidth,max height=\textheight]{figures/complexity/cw_literature/scribe.png}
      }
      \only<3>{
        \begin{adjustbox}{max totalsize={\textwidth}{\textheight},center}
        \begin{tikzpicture}[->,>=stealth',auto, node distance=4cm,
                            thick,transform shape]
          \node[state,label=above:{Described}]                       (A)                    {};
          \node[state,label=left:{Described written}]                (B) [below of=A]       {};
          \node[state,label=left:{Run Tests}]                        (D) [below of=B]       {};
          \node[state,label=below:{Described written buggy}]         (C) [below right of=D] {};
          \node[state,label=below:{Described written buggy}]         (E) [below left of=D]  {};

@@

\begin{frame}{Enhanced Cognition} % {Cab Drivers}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \only<2>{
  \begin{columns}
  \begin{column}{0.2\textwidth}
  \includegraphics[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \end{column}
  \begin{column}{0.8\textwidth}
  \includegraphics[width=\textwidth]{figures/complexity/brain_scans.png}
  \end{column}
  \end{columns}
  }
  \includegraphics<3>[width=\textwidth]{figures/photo/gps-map.jpg}
  \end{figure}
\end{frame}

\begin{frame}{Tracking Work and Workers} % {Algorithmic Measurement}
    % notes
    % \begin{itemize}
      \ali{Upwork's screen recording tool as a way to measure workers}
      % \item also maybe google analytics and other ways of tracking web--based workers
    % \end{itemize}
\end{frame}

>>>>

\begin{frame}{What Does On--Demand Work Say?}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      Build complexity into the process
      \begin{itemize}
        \item<+-> Apply CS methods to people\par
                 \scriptsize{\textcite{crowdForgeKittur}\par}\normalsize{}
        \item<+-> Humans as computational units\par
                 \scriptsize{\textcite{Lasecki:2014:LSR:2661334.2661352}\par}\normalsize{}
        \item<+-> Crowdsourcing workflows as function state machines\par
                 \scriptsize{\textcite{latoza2014microtask}\par}\normalsize{}
      \end{itemize}
    \end{column}

    \begin{column}{0.5\textwidth}
      \only<1>{
      \includegraphics[max width=\textwidth,max height=.9\textheight]{figures/complexity/cw_literature/mapReduce.png}
      }

      \only<2>{
        \includegraphics[max width=\textwidth,max height=.7\textheight]{figures/complexity/cw_literature/scribe.png}
      }
      \only<3>{
        \begin{adjustbox}{max totalsize={\textwidth}{.9\textheight},center}
        \begin{tikzpicture}[->,>=stealth',auto, node distance=4cm,
                            thick,transform shape]
          \node[state,label=above:{Described}]                       (A)                    {};
          \node[state,label=left:{Described written}]                (B) [below of=A]       {};
          \node[state,label=left:{Run Tests}]                        (D) [below of=B]       {};
          \node[state,label=below:{Described written buggy}]         (C) [below right of=D] {};
          \node[state,label=below:{Described written buggy}]         (E) [below left of=D]  {};

@@

\begin{frame}{Enhanced Cognition} % {Cab Drivers}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \only<2>{
  % \begin{columns}
  % \begin{column}{0.2\textwidth}
  % \includegraphics[width=\textwidth]{figures/photo/knowledge-student.jpg}
  % \end{column}
  % \begin{column}{0.8\textwidth}
  \includegraphics[width=\textwidth]{figures/complexity/brain_scansA.png}
  % \end{column}
  % \end{columns}
  }
  \includegraphics<3>[width=\textwidth]{figures/photo/gps-map.jpg}
  \end{figure}
\end{frame}

\begin{frame}{Tracking Work and Workers} % {Algorithmic Measurement}
\begin{columns}
\begin{column}{.5\textwidth}
\includegraphics[max width=\textwidth,max height=.8\textheight,keepaspectratio]{figures/screenshot_odeskteamapp.jpg}
\end{column}
\begin{column}{.5\textwidth}
% \begin{itemize}
  Upwork has turned to logging workers' keystrokes and taking screenshots automatically every 10 minutes
% \end{itemize}
% \includegraphics[max width=\textwidth,max height=.8\textheight,keepaspectratio]{figures/time-tracking-like-odesk-screenshot-monitor1.png}
\end{column}
\end{columns}

    % notes
    % \begin{itemize}
      % \ali{Upwork's screen recording tool as a way to measure workers}
      % \item also maybe google analytics and other ways of tracking web--based workers
    % \end{itemize}
\end{frame}
